---
title: "lesson_2_3_taylor_swift_day2"
format: html
---

```{r}
library(tidyverse)
```

# Question #5

## Step 1: Here's data for the whole population

```{r}
enjoyment_matrix =
  matrix(
    data = c(92, 89, 90, 88, 95, 100, 98, 93, 95, 84,
             82, 86, 90, 88, 86, 91, 90, 89, 85, 83,
             80, 74, 80, 67, 81, 82, 76, 77, 74, 65,
             72, 68, 74, 73, 70, 69, 72, 70, 68, 67,
             69, 67, 68, 68, 64, 66, 63, 63, 70, 68),
    nrow = 5,
    byrow = TRUE,
    dimnames = list("row" = 1:5, "column" = 1:10)
  )
enjoyment_matrix
```

It's nice to put the data in "long form" where each column is a variable.

```{r}
enjoyment_data =
  enjoyment_matrix |> 
  as_tibble() |>
  mutate(row = 1:5) |> 
  pivot_longer(!row, names_to = "column", values_to = "enjoyment") |> 
  mutate(column = as.integer(column))
enjoyment_data
```

Here's the true average enjoyment for the whole VIP section:

```{r}
true_average = enjoyment_data |> 
  pull(enjoyment) |> 
  mean()
```

## Step 2: Here are the 3 randomized sampling methods from last class

```{r}
run_SRS = function(i) {
  simple_random_sample =
    enjoyment_data |> 
    sample_n(10)
  simple_random_sample |> 
    pull(enjoyment) |> 
    mean()
}
run_stratified_by_col = function(i) {
  stratified_sample_by_col =
    enjoyment_data |>
    ## YOUR CODE HERE (copy-paste from above)
  group_by(column) |> 
  sample_n(1)
  stratified_sample_by_col |> 
    ## YOUR CODE HERE (copy-paste from above)
  pull(enjoyment) |> 
  mean()
}
run_stratified_by_row = function(i) {
  stratified_sample_by_row =
    enjoyment_data |>
    group_by(row) |> 
    sample_n(2)
  stratified_sample_by_row |> 
    ## YOUR CODE HERE (copy-paste from above)
  pull(enjoyment) |> 
  mean()
}
n_experiments = 100
srs_means = map_dbl(1:n_experiments, run_SRS)
stratified_by_row_means = map_dbl(1:n_experiments, run_stratified_by_row)
stratified_by_col_means = map_dbl(1:n_experiments, run_stratified_by_col)
experiment_results =
  tibble(
  "Simple random sample" = srs_means,
  "Stratified by row" = stratified_by_row_means,
  "Stratified by column" = stratified_by_col_means
) |> 
  pivot_longer(everything(), names_to = "method", values_to = "average_enjoyment")
experiment_results |> 
  ggplot(aes(x = average_enjoyment, fill = method)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = true_average, colour = "red") +
  facet_wrap(vars(method), ncol = 1) +
  theme(legend.position = "none")
```

## Step #3: Here are some more sampling methods

### Method #4: Cluster Random Sample (rows as clusters)

Pick all the data from one random row.

```{r}
row_cluster = sample(1:5, 1)
cluster_sample_by_row = enjoyment_data |> 
  filter(row %in% row_cluster)
cluster_sample_by_row
```

Calculate the mean for this sample:

```{r}
cluster_sample_by_row |> 
  pull(enjoyment) |> 
  mean()
```

Make a function for later:

```{r}
run_cluster_by_row = function(i) {
  row_cluster = sample(1:5, 1)
  cluster_sample_by_row = enjoyment_data |> 
    filter(row %in% row_cluster)
  cluster_sample_by_row |> 
    pull(enjoyment) |> 
    mean()
}
```

### Method #5:Cluster Random Sample (columns as clusters)

Randomly select 2 columns and ask everyone in those columns:

```{r}
col_cluster = sample(1:10, 2)
cluster_sample_by_col = enjoyment_data |> 
  filter(column %in% col_cluster)
cluster_sample_by_col
```

Calculate the mean for this sample:

```{r}
cluster_sample_by_col |> 
  pull(enjoyment) |> 
  mean()
```

Make a function for later:

```{r}
run_cluster_by_col = function(i) {
  col_cluster = sample(1:10, 2)
  cluster_sample_by_col = enjoyment_data |> 
    filter(column %in% col_cluster)
  cluster_sample_by_col |> 
    pull(enjoyment) |> 
    mean()
}
```

### Method #6: Systematic Random Sample

This code is confusing. Run everything, but don't worry about it too much!

Randomly sample the starting fan (out of all 50 fans).

```{r}
starting_fan_number = sample(1:50, 1)
starting_fan_number
```

Begin marking every 8th seat until you get to a sample of 10 seats (start back at the beginning if you need to)

```{r}
systematic_sample_numbers = ((starting_fan_number - 1 + 8*(0:9)) %% 50) + 1
systematic_sample_numbers
```

Collect enjoyment levels from those fans.

```{r}
systematic_sample = enjoyment_data[systematic_sample_numbers,]
systematic_sample
```

Calculate the eman enjoyment for those fans.

```{r}
systematic_sample |> 
  pull(enjoyment) |> 
  mean()
```

Make a function for later:

```{r}
run_systematic = function(i) {
  starting_fan_number = sample(1:50, 1)
  systematic_sample_numbers = ((starting_fan_number - 1 + 8*(0:9)) %% 50) + 1
  systematic_sample = enjoyment_data[systematic_sample_numbers,]
  systematic_sample |> 
    pull(enjoyment) |> 
    mean()
}
```

## Step 2: Run the experiments

```{r}
cluster_by_row_means = map_dbl(1:n_experiments, run_cluster_by_row)
cluster_by_col_means = map_dbl(1:n_experiments, run_cluster_by_col)
systematic_means = map_dbl(1:n_experiments, run_systematic)
cluster_by_row_means[1:10]
cluster_by_col_means[1:10]
systematic_means[1:10]
```

## Step 3: Graph the results of the experiments

```{r, message=FALSE}
experiment_results =
  tibble(
  "#1 Simple random sample" = srs_means,
  "#2 Stratified by row" = stratified_by_row_means,
  "#3 Stratified by column" = stratified_by_col_means,
  "#4 Cluster by row" = cluster_by_row_means,
  "#5 Cluster by column" = cluster_by_col_means,
  "#6 Systematic" = systematic_means
) |> 
  pivot_longer(everything(), names_to = "method", values_to = "average_enjoyment")

experiment_results |> 
  ggplot(aes(x = average_enjoyment, fill = method)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = true_average, colour = "red") +
  facet_wrap(vars(method), ncol = 2) +
  theme(legend.position = "none")
```
